\gettitle

### 2019-11-15 assignment2/submission2.tex
Expand and clarify solution to Problem 2.1

\section*{1 - Parameter Passing and RMI}
\subsection*{a)}
\begin{enumerate}[label=(\roman*)]
	\item 
	\item 
	\item 
\end{enumerate}

@@

@@

>>>>

\section*{1 - Parameter Passing and RMI}
\subsection*{a)}
\begin{enumerate}[label=(\roman*)]
	% no return value, so a is never changed
	\item \texttt{[1, 2, 3, 4, 5]}
	% the code given does not perform a swap, it only overwrites the lower indices with values from the upper ones.
	% because of reference semantics that overwrites the second input as well
	\item \texttt{[5, 4, 3, 4, 5]}
	\item \texttt{[5, 4, 3, 2, 1]} \emph{or} \texttt{[1, 2, 3, 4, 5]} \emph{or} \texttt{[5, 4, 3, 4, 5]}, depending on the exact semantic behaviour of the copy and restore operations.
	Given that the remote server passes the arguments by reference, the first question is whether \textit{x} and \textit{y} have separate copies of \textit{a}. 
	If they do, the first or second option is possible. 
	If there are no separate copies of \textit{a}, the procedure behaves as if the parameters were passed by reference. 
	Otherwise it depends on which value is restored first.
\end{enumerate}

@@

The result printed to the system console is:
\begin{verbatim}
$ java StringServer
1: B
2: BRS
3: ABSBRS
\end{verbatim}

We can deduce that all objects that extend UnicastRemoteObject are sent as reference, all other objects are sent as value.
In the first and last two lines the parameter is a StringBuffer object which does not implement UnicastRemoteObject and is therefore sent as value. 
In the third line the parameter is a StringServer object which does implement UnicastRemoteObject and because of this is sent as reference.

@@

The first line shows that even "complex java objects" are passed by value so long as they are not remote objects. 
This implies that even very large non-remote objects would be serialized and passed by value (e.g. Arrays with hundreds of thousands of elements).
Such a behaviour incurs large overheads, especially if only parts of the passed value are accessed by the remote procedure.

The lines two and three demonstrate the reference-passing behaviour within java's RMI implementation. 
Notably, remote objects are passed by reference. 
Calls to the passed remote objects are routed back to the JVM the actual object resides in. 
This can lead to large overheads if a lot of calls are made to the referenced object.
